Flesh Simulation in the Field of Animation

### 2020-02-24 LaTeX-Master-Vorlage/chapter/Introduction.tex
correcting stuff

\section{Motivation}
With steadily increasing computational power the demand of better results is constantly growing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
In the entertainment sector gaming industries and animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality. Both of them have made groundbreaking progress over the years. This is easily observed when we compare today's work with that from ten years ago.

As always we have different requirements for each use.
In some cases we want to exaggerate a movement or a reaction in a certain way. We can for example create a massive explosion in a movie that would not be half as spectacular in the real world.

In other scenarios we want to come as close as possible to reality. For instance we want an animated character to move and physically interact with its environment as a real human being would. Otherwise our brain would immediately recognize that some things do not add up.
The goal here is to bring characters quite literally to life. We can add small details like visible breathing and small wrinkles to have an even more convincing effect. The goal is to create the illusion of a character with personality, thought and emotions. In order to achieve this effect we need the character to move and react nearly physically correct.

In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} the authors addressed exactly the problem of making an animated movement of a human-like character look as natural as possible. In order to animate a physical movement we first need to understand the physics behind it which lies in the field of continuum mechanics. Unfortunately for most of us it has yet to be learned. The goal of this thesis is to give the necessary physical and mathematical background for a regular computer science student to understand the field of animation.

\section{Structure}
Following up I will give a brief overview of the necessary mathematical background and deliver an introduction in continuum mechanics. Next I will go through the ideas made in the paper mentioned and include some calculations and visualisations that help for a better understanding. \\

\todoredefined[inline]{
TODO: Improve intorduction (goals etc.). Adjust according to additions in text. Improve quote at beginning. Maybe add other applications as well (physical simulation) and how to go over to it?
}

>>>>

\section{Motivation}
With steadily increasing computational power, the demand of better results is constantly growing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
In the entertainment sector and gaming industry animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality. Both of them have made groundbreaking progress over the years. This is easily observed when we compare today's work with that from ten years ago.

As always, we have different requirements for each use.
In some cases we want to exaggerate a movement or a reaction in a certain way. We can for example create a massive explosion in a movie that would not be half as spectacular in the real world.

In other scenarios we want to come as close as possible to reality. For instance, we may want an animated character to move and physically interact with its environment as a real human being would. Otherwise, the human brain would immediately recognize that some things do not add up.
The goal here is to bring characters quite literally to life. We can add small details like visible breathing and small wrinkles to have an even more convincing effect. We aim to create the illusion of a character with personality, thought and emotions. In order to achieve this effect, we need the character to move and react physically correct.

In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}, the authors addressed exactly this problem of making an animated movement of a human-like character look as natural as possible. In order to animate a physical movement, we first need to understand the physics behind it which requires some knowledge in the field of continuum mechanics. Unfortunately, for most of us it has yet to be learned. The goal of this thesis is to give the necessary physical and mathematical background for a regular computer science student to understand the field of animation. In addition I will go deeper into the thematics of the paper mentioned before. I aim to get an understanding of their contribution in the field and implement their proposed energy myself.

\section{Structure}
In the following, I will give a brief overview of the necessary mathematical background and deliver an introduction into the field of continuum mechanics. Next, I will go through the ideas mentioned in the paper and include some calculations and visualisations that help for a better understanding. \\

\todoredefined[inline]{
TODO: Add goals in introduction. Adjust according to additions in text. Improve quote at beginning. Maybe add other applications as well (physical simulation) and how to go over to it?
}

### 2020-02-24 LaTeX-Master-Vorlage/glossary_and_acronyms.tex
correcting stuff

\newglossaryentry{berlin}{name={Berlin},description={Berlin ist die Bundeshauptstadt der Bundesrepublik Deutschland und zugleich eines ihrer Länder. Die Stadt Berlin ist mit über 3,4 Millionen Einwohnern die bevölkerungsreichste und mit 892 Quadratkilometern die flächengrößte Gemeinde Deutschlands sowie nach Einwohnern die zweitgrößte der Europäischen Union. Sie bildet das Zentrum der Metropolregion Berlin/Brandenburg (6 Millionen Einw.) und der Agglomeration Berlin (4,4 Millionen Einw.). Der Stadtstaat unterteilt sich in zwölf Bezirke. Neben den Flüssen Spree und Havel befinden sich im Stadtgebiet kleinere Fließgewässer sowie zahlreiche Seen und Wälder}}
\newglossaryentry{outsourcing}{name={Outsourcing},description={Outsourcing bzw. Auslagerung bezeichnet in der Ökonomie die Abgabe von Unternehmensaufgaben und -strukturen an externe oder interne Dienstleister. Es ist eine spezielle Form des Fremdbezugs von bisher intern erbrachter Leistung, wobei Verträge die Dauer und den Gegenstand der Leistung fixieren. Das grenzt Outsourcing von sonstigen Partnerschaften ab}}
\newglossaryentry{asp}{name={Application Service Providing},description={Der Application Service Provider (Abkürzung ASP) bzw. Anwendungsdienstleister ist ein Dienstleister, der eine Anwendung (z. B. ein ERP-System) zum Informationsaustausch über ein öffentliches Netz (z. B. Internet) oder über ein privates Datennetz anbietet. Der ASP kümmert sich um die gesamte Administration, wie Datensicherung, das Einspielen von Patches usw. Anders als beim Applikations-Hosting ist Teil der ASP-Dienstleistung auch ein Service (z.B. Benutzerbetreuung) um die Anwendung herum}}
\newglossaryentry{policy}{name={Policy},description={Im geschäftlichen Bereich bezeichnet Policy eine interne Leit- bzw. Richtlinie, die formal durch das Unternehmen dokumentiert und über ihr Management verantwortet wird}}
\newglossaryentry{pcie}{name={PCI Express},description={PCI Express („Peripheral Component Interconnect Express“, abgekürzt PCIe oder PCI-E) ist ein Standard zur Verbindung von Peripheriegeräten mit dem Chipsatz eines Hauptprozessors. PCIe ist der Nachfolger von PCI, PCI-X und AGP und bietet im Vergleich zu seinen Vorgängern eine höhere Datenübertragungsrate pro Pin.}}

\newacronym{cd}{CD}{Compact Disk}
\newacronym{lan}{LAN}{Local Area Network}
\newacronym{iso}{ISO}{Internationale Organisation für Normung}
\newacronym{sas}{SAS}{Serial Attached SCSI}
\newacronym{abbvz}{Abbvz.}{Abbildungsverzeichnis}

>>>>

\newglossaryentry{latex}
{
        name=latex,
        description={Is a mark up language specially suited for 
scientific documents}
}

\newacronym{gcd}{GCD}{Greatest Common Divisor}
\newacronym{svd}{SVD}{Singular Value Decomposition}
